% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[line]{res}
\usepackage{hyperref}
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}
\name{Nathaniel Case \left<\href{mailto:Qalthos@gmail.com}{Qalthos@gmail.com}\right>}

\address{131 Countess Drive\\West Henrietta, NY 14586\\585-210-8920}

\begin{resume}

\section{OBJECTIVE}
    Seeking to do neat things in interesting ways.

\section{EDUCATION}
    Rochester Institute of Technology, Rochester, NY \\
    BS in Computer Science | G.P.A. 3.48/4.0

\section{LANGUAGES AND TECHNOLOGIES}
    \begin{tabular}{l c l l c l}
        Python & ● ● ● ● ○ && Version Control & ● ● ● ● ○ & (+1 to git)\\
        HTML & ● ● ● ● ○ && Web Frameworks & ● ● ● ○ ○ & (+1 to Flask, TurboGears, Pyramid)\\
        CSS & ● ● ● ○ ○ && Web Scraping & ● ● ● ● ○ & (+1 to BeautifulSoup)\\
        Javascript & ● ● ○ ○ ○ & (+1 to jQuery)\\
        Java & ● ● ● ○ ○\\
        Bash & ● ● ● ○ ○\\

    \end{tabular}

\section{OPEN SOURCE PROJECTS}
    \begin{format}
        \title{l}\employer{l}\dates{r}\\
        %\location{l}\\
        \body
    \end{format}

    \title{infoboard}
    \employer{\href{http://github.com/FOSSRIT/infoboard}{github.com/FOSSRIT/infoboard}}
    \dates{2012 - present}
    \location{Python, Twisted, GTK3, SQLAlchemy, Requests}
    \begin{position}
        Desktop app to track Github contributions in (near) real-time.
    \end{position}

    \title{Remysmoke}
    \employer{\href{http://github.com/Qalthos/remysmoke}{github.com/Qalthos/remysmoke}}
    \dates{2011 - present}
    \location{Python, TurboGears2, ToscaWidgets2, OpenShift}
    \begin{position}
        A web tracker to watch smoking habits.
        (\url{http://remysmoke.linkybook.com/})
    \end{position}

    \title{Election Dashboard}
    \employer{\href{http://github.com/FOSSRIT/monroe-elections}{github.com/FOSSRIT/monroe-elections}}
    \dates{2010 - present}
    \location{Python, BeautifulSoup, Twisted, HTML5, jQuery}
    \begin{position}
        A dashboard displaying live results from elections in NY.
        (\url{http://foss.rit.edu/election/})
    \end{position}

    \title{GrooveBot}
    \employer{\href{http://github.com/Qalthos/groovebot}{github.com/Qalthos/groovebot}}
    \dates{2010 - present}
    \location{Python, Twisted}
    \begin{position}
        An IRC bot that takes song requests and plays them over shared speakers.
    \end{position}

    \title{CIVX}
    \employer{\href{https://fedorahosted.org/civx/}{fedorahosted.org/civx}}
    \dates{2010 - 2011}
    \location{Python, TurboGears2, Moksha, jQuery}
    \begin{position}
        A web platform for civic engagement and inspection.
        (\url{http://civx.us/})
    \end{position}

    More projects available at \url{http://github.com/Qalthos}

\section{WORK EXPERIENCE}
    \begin{format}
        \title{l}\employer{r}\\
        \location{l}\dates{r}\\
        \body
    \end{format}

    \title{Lead Student Developer}
    \employer{Lab for Technological Literacy, RIT}
    \dates{June 2010 - Present}
    \location{Rochester, NY}
    \begin{position}
        Worked on many projects in software (some listed above), instructed
        people, and managed the physical space of the FOSSBox.
    \end{position}

    \title{Informatics Co-op}
    \employer{Strong Memorial Hospital}
    \dates{June 2009 - May 2010}
    \location{Rochester, NY}
    \begin{position}
        Worked with researchers to transfer legacy paper forms to Teleforms OCR
        forms, web-accessible forms through ColdFusion, or Java applets.
    \end{position}

    \title{Software Co-op}
    \employer{MOOG Inc.}
    \dates{August 2008 - November 2008}
    \location{East Aurora, NY}
    \begin{position}
        Maintained and deployed a variety of web applications using J2EE,
        Struts, AJAX, and SQL
    \end{position}

\section{HONORS}
    Dean's List: Spring, Fall 2007, Winter, Spring 2008, Spring 2010 \\
    National Honor Socierty 2006 \\
    BSA Eagle Scout Award 2006 \\
    TIME Magazine Person of the Year 2006

\end{resume}

\end{document}
